{ \centering Scientific Report - Summary of Research\\ ~\\ Automatized compilation of sequential software to a diverse set of hardware accelerators\\ } ~\\ \vspace{18em} \large Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
deploy: 0f462f07ae66d814c22a2432d8a25851cde7a270

In the following, we discuss four milestones we identified as important to
reach these goals:

@@

>>>>

In the following, we discuss five milestones we identified as important to
reach these goals:

@@

Overall, this project developed important scientific ideas and made many of
them available in a production compiler setting via the MLIR project. In
particular, the LLVM project now has a modern and fast polyhedral library,
a generic GPU backend, a Verilog compiler. These components have been
tested in various combinations to accelerate climate science, deep neural
networks, and a number of general-purpose codes. We believe this project
made critical advances towards its goal of automating the generation
of high-performance code.

The PI moved to an associate professor position, the staff on this project
moved to PhD and industry positions working on projects directly related
to ideas from this proposal, and three of our interns are taking up a
new PhD position with the PI himself.
